The Unicode Cookbook \linebreak for Linguists

### 2018-01-13 book/chapters/_remove/originaltext.tex
issues in chapter 2

The Unicode Standard represents a massive step forward because it aims to eradicate the distinction between `universal' (ASCII) versus `language/resource-particular' (Font) by adding as much as possible language-specific information into the universal standard. However, there are still language/resource-specific specifications necessary for the proper usage of Unicode, as will be discussed below. Within the Unicode structure many of these specifications can be captured by so-called `Locales' or `Locale Descriptions', so we are moving to a new distinction of `universal' (Unicode Standard) versus `language-particular' (Locale Description). The major gain is a much larger compatibility on the universal level (because Unicode standardizes a much larger portion of writing system diversity), and much better possibilities for automatic processing on the language-particular level (because Locale Descriptions are computer readable specifications).

@@

For the automatic processing of the profiles, the following technical standards will be expected:
\begin{enumerate}
	\def\labelenumi{\arabic{enumi}.} 
	\item \textsc{Each line of a profile will be interpreted as a regular expression. }Software applications using profiles can also offer to interpret a profile in the literal sense to avoid the necessity for the user to escape regular expressions metacharacters in the profile. However, this only is possible when no contexts or classes are described, so this seems only useful in the most basic orthographies. 
	\item \textsc{The `class' column will be used to produce explicit ``or'' chains of regular expressions}, which will then be inserted in the `graphemes', `left' and `right' columns at the position indicated by the class-identifiers. For example, a class ``V'' as a context specification might be replaced by a regular expression like ``(a\textbar{}e\textbar{}i\textbar{}o\textbar{}u\textbar{}ei\textbar{}au)''. Only the graphemes themselves are included here, not any contexts specified for the elements of the class. 
	\item \textsc{The `left' and `right' contexts will be included into the regular expressions by using lookbehind and lookahead}. Basically, the actual regular expression syntax of lookbehind and lookahead is simply hidden to the users by allowing them to only specify the contexts themselves. Internally, the contexts in the columns ``left'' and ``right'' are combined with the column ``graphemes'' to form a complex regular expression like ``(?\textless{}=left)graphemes(?=right)''. 
	\item \textsc{The regular expressions will be applied in the order as specified in the profile, from top to bottom.} A software implementation can offer help in figuring out the optimal ordering of the regular expressions, but should then explicitly report on the order used. 
\end{enumerate}

>>>>

The Unicode Standard represents a massive step forward because it aims to eradicate the distinction between `universal' (ASCII) versus `language/resource-particular' (Font) by adding as much as possible language-specific information into the universal standard. However, there are still language/resource-specific specifications necessary for the proper usage of Unicode, as will be discussed below. Within the Unicode structure many of these specifications can be captured by so-called `Locales' or `Locale Descriptions', so we are moving to a new distinction of `universal' (Unicode Standard) versus `language-particular' (Locale Description). The major gain is a much larger compatibility on the universal level (because Unicode standardizes a much larger portion of writing system diversity), and much better possibilities for automated processing on the language-particular level (because Locale Descriptions are computer readable specifications).

@@

For the automated processing of the profiles, the following technical standards will be expected:
\begin{enumerate}
	\def\labelenumi{\arabic{enumi}.} 
	\item \textsc{Each line of a profile will be interpreted as a regular expression. }Software applications using profiles can also offer to interpret a profile in the literal sense to avoid the necessity for the user to escape regular expressions metacharacters in the profile. However, this only is possible when no contexts or classes are described, so this seems only useful in the most basic orthographies. 
	\item \textsc{The `class' column will be used to produce explicit ``or'' chains of regular expressions}, which will then be inserted in the `graphemes', `left' and `right' columns at the position indicated by the class-identifiers. For example, a class ``V'' as a context specification might be replaced by a regular expression like ``(a\textbar{}e\textbar{}i\textbar{}o\textbar{}u\textbar{}ei\textbar{}au)''. Only the graphemes themselves are included here, not any contexts specified for the elements of the class. 
	\item \textsc{The `left' and `right' contexts will be included into the regular expressions by using lookbehind and lookahead}. Basically, the actual regular expression syntax of lookbehind and lookahead is simply hidden to the users by allowing them to only specify the contexts themselves. Internally, the contexts in the columns ``left'' and ``right'' are combined with the column ``graphemes'' to form a complex regular expression like ``(?\textless{}=left)graphemes(?=right)''. 
	\item \textsc{The regular expressions will be applied in the order as specified in the profile, from top to bottom.} A software implementation can offer help in figuring out the optimal ordering of the regular expressions, but should then explicitly report on the order used. 
\end{enumerate}

### 2018-01-13 book/chapters/_remove/terminology.tex
issues in chapter 2

The Unicode Standard represents a massive step forward because it aims to
eradicate the distinction between \textsc{universal} (ASCII) versus
\textsc{language/resource-particular} (Font) by adding as much as possible
language-specific information into the universal standard. However, there are
still language/resource-specific specifications necessary for the proper usage
of Unicode, as will be discussed below. Within the Unicode structure many of
these specifications can be captured by so-called \textsc{Locale Descriptions}
or simply locales, so we are moving to a new distinction of universal (Unicode
Standard) versus language-particular (Locale Description). The major gain is a
much larger compatibility on the universal level (because Unicode standardizes a
much larger portion of writing system diversity), and much better possibilities
for automatic processing on the language-particular level (because Locale
Descriptions are computer readable specifications).

>>>>

The Unicode Standard represents a massive step forward because it aims to
eradicate the distinction between \textsc{universal} (ASCII) versus
\textsc{language/resource-particular} (Font) by adding as much as possible
language-specific information into the universal standard. However, there are
still language/resource-specific specifications necessary for the proper usage
of Unicode, as will be discussed below. Within the Unicode structure many of
these specifications can be captured by so-called \textsc{Locale Descriptions}
or simply locales, so we are moving to a new distinction of universal (Unicode
Standard) versus language-particular (Locale Description). The major gain is a
much larger compatibility on the universal level (because Unicode standardizes a
much larger portion of writing system diversity), and much better possibilities
for automated processing on the language-particular level (because Locale
Descriptions are computer readable specifications).
